### 2021-03-08 input/background.tex
maybe start by defining scoped broadcast

\begin{definition}[Fog infrastructure]
  A fog infrastructure is a \underline{g}raph $G(V, E)$ of
  \underline{v}ertices $V$ and bidirectional \underline{e}dges $E \in
  V \times V$. Edges have symmetric \underline{w}eights $w_{ij} =
  w_{ji}$ with $i, j \in V$.
\end{definition}

>>>>

\begin{definition}[Fog infrastructure]
  A fog infrastructure is a connected \underline{g}raph $G(V, E)$ of
  \underline{v}ertices $V$ and bidirectional \underline{e}dges $E \in
  V \times V$. Edges have symmetric \underline{w}eights $w_{ij} =
  w_{ji}$ with $i, j \in V$.
\end{definition}

Processes can send messages to their neighboring processes. Processes
can reliably broadcast messages by forwarding delivered
messages~\cite{nedelec2018causal,raynal2013distributed}. However,
reliable broadcast definition states that \emph{all} correct processes
should deliver broadcast messages. This proves costly in large scale
systems comprising thousands of processes. Instead, we define
\emph{scoped broadcast} where messages reach only interested
processes, significantly reducing generated traffic.

\begin{definition}[Scoped broadcast]
  \TODO{meow predicate, meow path, meow state, meow message.}
\end{definition}

This definition highlights the transitive relevance of sent messages
and encompasses more specific definitions of related
work~\cite{hsiao2005scoped,lue2006scoped,wang2015prodiluvian}.  A
process from Paris could scoped broadcast a message to all processes
in this city. A process from Paris could scoped broadcast a message to
all processes in this city plus neighboring cities by overloading
forwarded messages the first time they reach another city. As for
reliable broadcast, there exists different trade-off on space, time,
and communication.
